---
title: "Introducing 'kinlab' --\\newline \\normalsize{Analyzing Kinship and Reproduction in historical family data from the Krummhörn (Germany, 18th and 19th centuries)}"
author: "Johannes Johow"
date: "May 13th, 2015"
output: rmarkdown::tufte_handout
---

# Introduction

The Krummhörn is a North-Western region in Germany being already populated since the Middle Age and primarly because of it's fertile marsh yields to an above-average agricultural productivity. During the early 1980's, Eckart Voland[^Voland_site] initiated a long-term study for the reconstitution of families in the 18th and 19th centuries population of the _Krummhörn_ making use of methods from historical demography[^Voland_2000]  
 

```{r, fig.fullwidth = TRUE, fig.width=20, fig.height=10, fig.cap = paste0("Pedigree of mother ", as.numeric( names(kh.data::kh_ped)[1]),", on", kinlab::as_date(kh.data::kh_mat[names(kh.data::kh_ped)[1],2,1]))}
kinlab::plot_pedigree(as.numeric( names(kh.data::kh_ped)[1]), kinlab::as_date(kh.data::kh_mat[names(kh.data::kh_ped)[1],2,1]), as.data.frame(kh.data::kh_ind),  kh.data::kh_ped[[1]],
kh.data::kh_mat, cex = 0.6)
```

# Headings

This style provides a- and b-heads (that is, `#` and `##`), demonstrated above.
An error is emitted if you try to use `###` and smaller headings.

\newthought{In his later books}[^books_be], Tufte starts each section with a bit of vertical space, a non-indented paragraph, and sets the first few words of the sentence in small caps. To accomplish this using this style, use the `\newthought` command as demonstrated at the beginning of this paragraph.

# Figures

## Margin Figures

Images and graphics play an integral role in Tufte's work. To place figures or tables in the margin you can use the `fig.margin` knitr chunk option. For example:

```{r, fig.fullwidth = TRUE, fig.width=14, fig.width=10, fig.cap = paste0("A kin map for mother ", as.numeric( names(kh.data::kh_ped)[1]),", on ", kinlab::as_date(kh.data::kh_mat[names(kh.data::kh_ped)[1],2,1]), ".")}

kinlab::plot_kinmap(id=as.numeric( names(kh.data::kh_ped)[1]),
                      evdat= kinlab::as_date(kh.data::kh_mat[names(kh.data::kh_ped)[1],2,1]),
                      list_kin=kh.data::kh_kin,
                      list_geo=kh.data::kh_geo,
                      my_map=kh.data::kh_geo[[2]][[1]],
                      spit_results=FALSE,
                      throw_plots=TRUE)
```


Note the use of the `fig.cap` chunk option to provide a figure caption. You can adjust the proportions of figures using the `fig.width` and `fig.height` chunk options. These are specified in inches, and will be automatically scaled down to fit within the handout margin.

## Equations

You can also include \LaTeX\ equations in the margin by explicitly invoking the `marginfigure` environment.

\begin{marginfigure}
$$\frac{d}{dx}\left( \int_{0}^{x} f(u)\,du\right)=f(x).$$
\caption{An equation}
\end{marginfigure}

Note the use of the `\caption` command to add additional text below the equation.

## Full Width Figures

You can arrange for figures to span across the entire page by using the `fig.fullwidth` chun

Note the use of the `fig.width` and `fig.height` chunk options to establish the proportions of the figure. Full width figures look much better if their height is minimized.

## Main Column Figures

Besides margin and full width figures, you can of course also include figures constrained to the main column.

# Sidenotes

One of the most prominent and distinctive features of this style is the extensive use of sidenotes. There is a wide margin to provide ample room for sidenotes and small figures. Any use of a footnote will automatically be converted to a sidenote. ^[This is a sidenote that was entered using a footnote.] 

If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `\marginnote` command. \marginnote{This is a margin note.  Notice that there isn't a number preceding the note.}

Note also that the two footnote references (`tufte_latex` and `books_be`, both defined below) were also included in the margin on the first page of this document.

# Tables

You can use the **xtable** package to format \LaTeX\ tables that integrate well with the rest of the Tufte handout style. Note that it's important to set the `xtable.comment` and `xtable.booktabs` options as shown below to ensure the table is formatted correctly for inclusion in the document.

[^Voland_2000]: http://onlinelibrary.wiley.com/doi/10.1002/1520-6505(2000)9:3%3C134::AID-EVAN3%3E3.0.CO;2-M/abstract
[^Voland_site]: https://scholar.google.com/citations?user=QOp-OK8AAAAJ&hl=en

